E1 Extras

### 2024-03-13 Analysis/e1_Analysis.qmd
re-render e1 appendix

```{r setup, echo=FALSE, include=FALSE}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
quietly( source(here::here("Functions", "packages.R")))

@@

@@

```{r}
#| fig-cap: "Mean Vx over training blocks"
#| fig-width: 10
#| fig-height: 9
#| tbl-cap: "test table"

# vpt1=plotWithTable(vp1,vt1,arrange="V")
nb=5
vp1=e1 |> filter(expMode=="train") |> learn_curve_plot(gt.train,vx,condit,facet_var=vb,groupVec=c(gt.train,condit,tOrder,id,vb),nbins=nb)
vp1

@@

```{r}
#| fig-cap: "Absolute Deviation from Band over training"
#| fig-width: 8

vp2=e1 |> filter(expMode=="train") |> 
  learn_curve_plot(gt.train,dist,condit,facet_var=vb,groupVec=c(gt.train,condit,tOrder,id,vb),nbins=nb) 
vp2

@@

```{r}
#| fig-cap: "Signed Deviation from Band over training"
#| fig-width: 8

vp3=e1 |> filter(expMode=="train") |> learn_curve_plot(gt.train,sdist,condit,facet_var=vb,groupVec=c(gt.train,condit,tOrder,id,vb),nbins=nb) 
vp3

@@

# 22
::: {.column-page-right}
```{r}
#| layout: [[65, 65],[-5], [1,550, 550]]
#| label: train tables2
#| echo: fenced
#| tbl-subcap: 
#|   - "Vx"
#|   - "Deviation from target"

vt1 %>% kable(format = "html",escape = FALSE)
vt2 %>% kable(format = "html",escape = FALSE)

@@

# 33
```{r}
#| layout: [[65, 65],[-5], [1,350, 350,10]]
#| label: train tables
#| echo: fenced
#| tbl-subcap: 
#|   - "Vx"
#|   - "Deviation from target"
#| column: screen-inset-right

vt1 %>% kable(format = "html",escape = FALSE)
vt2 %>% kable(format = "html",escape = FALSE)

@@

```{r}
#| label: tbl-example4
#| tbl-cap: "Example"
#| tbl-subcap: 
#|   - "Signed Distance"
#|   - "Percent Hit"
#| layout: [[80, 90],[2], [-60,650]]
#| echo: fenced
#| column: screen-inset-right
#| fig-width: 14
#|

@@

```{r}
#| fig-width: 12
#| fig-height: 11
#| column: page-inset-right
((vp1+big_text()+vp2+big_text())/(vp3+big_text()+vp4+big_text())) + plot_layout(guides = "collect")

>>>>

```{r setup, echo=FALSE, include=FALSE}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist, modelsummary)
e1 <- readRDS(here("data/e1_08-21-23.rds"))
quietly( source(here::here("Functions", "packages.R")))

@@

::: {.column-page-right}
```{r}

plot_violin_condit <- function(fcondit, fvb, pvar) {

  full_range <- testAvg |> pull({{pvar}}) |> range(na.rm=TRUE)
  testAvg |>
    filter(condit == fcondit, vb==fvb) |> 
    ggplot(aes(.data[[pvar]])) +
    geom_density(fill = 'dodgerblue4') +
    theme_void() +
    coord_cartesian(xlim = full_range)
}

unique_combinations = testAvg |> ungroup() |>
  distinct(condit, vb)

testAvg |> group_by(condit,vb) |> 
  summarize(mean=mean(dist),sd=sd(dist)) |> 
  mutate(Distribution=vb) |> 
  gt() |>
  tab_spanner(
    label = 'Training Condit',
    columns = -condit
  ) |> 
  cols_label_with(fn = str_to_title) |> 
  fmt_number(decimals = 2) |> 
  cols_align('left', columns = condit) |> 
  text_transform(
    locations = cells_body(columns = 'Distribution'),
    fn = function(column) {
      map2(unique_combinations$condit, unique_combinations$vb,~plot_violin_condit(.x,.y,'vx')) |>
        ggplot_image(height = px(50), aspect_ratio = 3)
    }
  )

vars_to_plot <- c('dist', 'vx')

tables <- map(vars_to_plot, function(pvar) {
  testAvg |>
    group_by(condit, vb) |>
    summarize(mean = mean(.data[[pvar]]), sd = sd(.data[[pvar]])) |>
    mutate(Distribution = vb) |>
    gt() |>
    tab_spanner(
      label = 'Training Condit',
      columns = -condit
    ) |>
    cols_label_with(fn = str_to_title) |>
    fmt_number(decimals = 2) |>
    cols_align('left', columns = condit) |>
    text_transform(
      locations = cells_body(columns = 'Distribution'),
      fn = function(column) {
        map2(unique_combinations$condit, unique_combinations$vb, ~plot_violin_condit(.x, .y, pvar)) |>
          ggplot_image(height = px(50), aspect_ratio = 3)
      }
    )
})
#print(tables[[1]])
#print(tables[[2]])

library(gtExtras)
gt_two_column_layout(tables)

```{r fig.width=12, fig.height=11}

#https://modelsummary.com/articles/datasummary.html

datasummary(vx*vb ~ Mean + SD + Histogram, data = testAvg)
datasummary(vx*vb*condit ~ Mean + SD + Histogram, data = testAvg)

datasummary(vx*vb*condit ~ Mean + SD + Histogram, data = test)

datasummary_crosstab(vb ~ condit * tOrder, data = test)

datasummary_crosstab(result ~ condit,
                     statistic = 1 ~ Percent("col"),
                     data = test)

datasummary_crosstab(result ~ condit*vb,
                     statistic = 1 ~ Percent("col"),
                     data = test)

datasummary(vx+dist+vy ~ mean *condit*vb,
            data = e1)

datasummary(Heading("X Velocity")*vx+Heading("Abs. Deviation")*dist+vy ~ mean *condit*vb,
            data = e1)

datasummary(vx + dist ~ Factor(condit) * (mean + sd),
            data = test)

datasummary(vx + dist ~ Factor(condit)*vb * (mean + sd),
            data = test)

datasummary(vb*Factor(condit) * (mean + sd) ~ vx + dist,
            data = test)

tmp <- mtcars[, c("mpg", "hp")]

# create a list with individual variables
# remove missing and rescale
tmp_list <- lapply(tmp, na.omit)
tmp_list <- lapply(tmp_list, scale)

# create a table with `datasummary`
# add a histogram with column_spec and spec_hist
# add a boxplot with colun_spec and spec_box
emptycol = function(x) " "
datasummary(mpg + hp ~ Mean + SD + Heading("Boxplot") * emptycol + Heading("Histogram") * emptycol,
    output = "kableExtra",
    data = tmp) %>%
    kableExtra::column_spec(column = 4, image = spec_boxplot(tmp_list)) %>%
    kableExtra::column_spec(column = 5, image = spec_hist(tmp_list))

tmp_list <- lapply(test |> ungroup() |> select(vx,vb,condit), na.omit)
# scale only numeric columns - not all are numeric so can't just lapply

tmp_list <- map(tmp_list, ~if(is.numeric(.x)) scale(.x) else .x)

ts=test |> ungroup() |> select(vx,vb,condit) |> mutate(vxScale=scale(vx)[,1])

 datasummary(vxScale*vb ~  Mean + Histogram,
            data=ts, output = "kableExtra")  %>%
    kableExtra::column_spec(column = 4, image = spec_boxplot(ts))

datasummary(vx*vb ~  Mean + Median+ SD + Histogram,
            data=test, output = "markdown")

datasummary(dist*vb ~  Mean + Median+ SD + Histogram,
            data=test, output = "markdown")

datasummary(vx*vb*condit ~  Mean + Histogram,
            data=test, output = "kableExtra")  %>%
    kableExtra::column_spec(column = 5, image = spec_boxplot(tmp_list))

cap <- "Testing - No Feedback"
f <- (`Condit` = condit) ~ (` ` = vx) * (`Distribution` = Histogram) + vx * vb * ((`Avg.` = Mean)*Arguments(fmt='%.0f') + (`SD` = SD)*Arguments(fmt='%.0f'))

datasummary(f,
            data = test,
            output = 'gt',
            title = cap,
            notes = 'Artwork by @Thomas',
            sparse_header = TRUE)

f <- (`Band` = vb) ~ (` ` = vx) * (`Distribution` = Histogram) + vx * condit * ((`Avg.` = Mean)*Arguments(fmt='%.0f') + (`SD` = SD)*Arguments(fmt='%.0f'))

datasummary(f,
            data = test,
            output = 'gt',
            title = cap,
            notes = 'Artwork by @Thomas',
            sparse_header = TRUE)

f <- (`Band` = vb) ~ (` ` = vx) * (`Distribution` = Histogram) + vx * condit * expMode2 * ((`Avg.` = Mean)*Arguments(fmt='%.0f') + (`SD` = SD)*Arguments(fmt='%.0f'))

datasummary(f,
            data = e1,
            output = 'gt',
            sparse_header = TRUE)

f <- (`Band` = vb)* expMode2 ~ vx * condit  * ((`Avg.` = Mean)*Arguments(fmt='%.0f') + (`SD` = SD)*Arguments(fmt='%.0f'))

datasummary(f,
            data = e1,
            output = 'gt',
            sparse_header = TRUE)

f <- (`Band` = vb)* expMode2 ~ dist * condit  * ((`Avg.` = Mean)*Arguments(fmt='%.0f') )

datasummary(f,
            data = e1,
            output = 'gt',
            sparse_header = TRUE) 
```

@@

```{r}
#| fig-cap: "Mean Vx over training blocks"
#| fig-width: 10
#| fig-height: 9
#| tbl-cap: "test table"
#| eval: false
# vpt1=plotWithTable(vp1,vt1,arrange="V")
nb=5
vp1=e1 |> filter(expMode=="train") |> learn_curve_plot(gt.train,vx,condit,facet_var=vb,groupVec=c(gt.train,condit,tOrder,id,vb),nbins=nb)
vp1

@@

```{r}
#| fig-cap: "Absolute Deviation from Band over training"
#| fig-width: 8
#| eval: false
#| 
vp2=e1 |> filter(expMode=="train") |> 
  learn_curve_plot(gt.train,dist,condit,facet_var=vb,groupVec=c(gt.train,condit,tOrder,id,vb),nbins=nb) 
vp2

@@

```{r}
#| fig-cap: "Signed Deviation from Band over training"
#| fig-width: 8
#| eval: false
vp3=e1 |> filter(expMode=="train") |> learn_curve_plot(gt.train,sdist,condit,facet_var=vb,groupVec=c(gt.train,condit,tOrder,id,vb),nbins=nb) 
vp3

@@

# 22
::: {.column-page-right}
```{r}
#| layout: [[65, 65],[-5], [1,550, 550]]
#| label: train tables2
#| echo: fenced
#| tbl-subcap: 
#|   - "Vx"
#|   - "Deviation from target"
#| eval: false
#| 
vt1 %>% kable(format = "html",escape = FALSE)
vt2 %>% kable(format = "html",escape = FALSE)

@@

# 33
```{r}
#| layout: [[65, 65],[-5], [1,350, 350,10]]
#| label: train tables
#| echo: fenced
#| tbl-subcap: 
#|   - "Vx"
#|   - "Deviation from target"
#| column: screen-inset-right
#| eval: false
vt1 %>% kable(format = "html",escape = FALSE)
vt2 %>% kable(format = "html",escape = FALSE)

@@

```{r}
#| label: tbl-example4
#| tbl-cap: "Example"
#| tbl-subcap: 
#|   - "Signed Distance"
#|   - "Percent Hit"
#| layout: [[80, 90],[2], [-60,650]]
#| echo: fenced
#| column: screen-inset-right
#| fig-width: 14
#| eval: false

@@

```{r}
#| fig-width: 12
#| fig-height: 11
#| column: page-inset-right
#| eval: false
((vp1+big_text()+vp2+big_text())/(vp3+big_text()+vp4+big_text())) + plot_layout(guides = "collect")
